The Effect of Word Alignments in Bilingual and Monolingual Post-Editing

### 2015-02-27 paper/paper_methodology.tex
More work

\begin{table*}[t]
\begin{subtable}[b]{.5\linewidth}
\begin{center}
\begin{tabular} { | c | p{66mm} | }
\hline
  12 & The post-edited translation is superior to the reference translation \\ \hline
  10 & The meaning of the Russian sentence is fully conveyed in the English translation \\ \hline
  8 & Most of the meaning of the Russian sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Russian sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Russian sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\caption{Russian-English}
\end{subtable}
\begin{subtable}[b]{.5\linewidth}
\begin{center}
\begin{tabular} { | c | p{66mm} | }
\hline
  10 & The meaning of the Spanish sentence is fully conveyed in the English translation \\ \hline
%  9 & The English translation contains one minor error \\ \hline
  8 & Most of the meaning of the Spanish sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Spanish sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Spanish sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\caption{Spanish-English}
\label{judge_guidelines_spanish}
\end{subtable}
\caption{Adequacy evaluation guidelines for bilingual Russian-English human judges \citep{2014_WMT_Schwartz_etal}, and for bilingual Spanish-English human judges. Because no reference translation was available for Spanish-English, the 12 category is omitted.}
\label{judge_guidelines}
\end{table*}

\subsection{Participants}

There were six participants who served as post-editors in this study, all of whom were paid for their time.
%
These participants were all English-Russian bilinguals.
%
Four of the six bilingual participants (PE2, PE3, PE4, \& PE6) had Russian as their first language (L1) and were highly proficient in English as their second language (L2).
%
The other two bilingual participants (PE1 \& PE5) had English as their first language and were highly proficient in Russian as their second language.
%
Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a Russian Translation program at an American university. %and three were undergraduate students in the same program.
%a Russian Translation program at the same American university.

@@

\todo[inline]{Add Spanish paragraph here}

\subsection{Materials}

@@

\todo[inline]{Add Spanish paragraph here}

@@

\todo[inline]{Add Spanish paragraph here}

@@

Participants performed the test individually in an office setting and were instructed to minimally post-edit. 
%
Specifically, they were asked to disregard issues of style and to focus on 
%
a) how well the translation conveyed the meaning of the source text, and 
%
b) the grammatical correctness of the translated segments. 
%
Participants sat in front of a computer that displayed the source texts divided up into segments \cite[Figure 1]{2014_WMT_Schwartz_etal}. % (see \citet{2014_WMT_Schwartz_etal}).
%
Directly below each source text segment, its machine translation was displayed.
%
Below that was an active response area, where participants were asked to carry out the post-editing.
%
The only data collected was the final post-edited output and the overall time taken per text.

\todo[inline]{Add Spanish paragraph here}

>>>>

\begin{table*}[t]
\begin{subtable}[b]{.5\linewidth}
\begin{center}
\begin{tabular} { | c | p{66mm} | }
\hline
  12 & The post-edited translation is superior to the reference translation \\ \hline
  10 & The meaning of the Russian sentence is fully conveyed in the English translation \\ \hline
  8 & Most of the meaning of the Russian sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Russian sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Russian sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\caption{Russian-English}
\label{judge_guidelines_russian}
\end{subtable}
\begin{subtable}[b]{.5\linewidth}
\begin{center}
\begin{tabular} { | c | p{66mm} | }
\hline
  10 & The meaning of the Spanish sentence is fully conveyed in the English translation \\ \hline
%  9 & The English translation contains one minor error \\ \hline
  8 & Most of the meaning of the Spanish sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Spanish sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Spanish sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\caption{Spanish-English}
\label{judge_guidelines_spanish}
\end{subtable}
\caption{Adequacy evaluation guidelines for bilingual Russian-English human judges \citep{2014_WMT_Schwartz_etal}, and for bilingual Spanish-English human judges \citep{2009_EACL_Albrecht_etal}. Because no reference translation was available for Spanish-English, the 12 category is omitted.}
\label{judge_guidelines}
\end{table*}

\subsection{Russian-English Bilingual Participants}
There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time.
%
These participants were all English-Russian bilinguals.
%
Four of the six bilingual participants (PE2, PE3, PE4, \& PE6) had Russian as their first language (L1) and were highly proficient in English as their second language (L2).
%
The other two bilingual participants (PE1 \& PE5) had English as their first language and were highly proficient in Russian as their second language.
%
Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a university Russian Translation program. %and three were undergraduate students in the same program.
%a Russian Translation program at the same American university.

@@

\subsubsection{Spanish-English Bilingual Participants}

There were four participants (PE7, PE8, PE9, PE10) who served as post-editors in this portion of the study, all of whom were paid for their time. 
%
They were all Spanish-English bilinguals with English as their first language (L1) and highly proficient in Spanish as their second language (L2). 
%
The four were second year students in a university Master of Spanish Translation program.

\subsection{Russian Data}

@@

\input{alignments_true}

\subsection{Spanish Data}

Two Spanish source texts were selected. Both were extracts from a news article from a Spanish newspaper covering current world news events. 
%
The two texts were divided up into segments that corresponded to sentences or stand alone phrases. 
%
The first text (Doc C) had 26 segments that varied in length from 4 to 24 words (mean length 15 words) and the second text (Doc D) had 25 segments that varied in length from 4 to 28 words (mean length 16 words).
%
No reference translations exist for either Spanish text.

The Spanish source texts were translated automatically using the Microsoft Bing Translator through its online developer API.
%
Bing Translator, when accessed via the developer API, can be configured to return character-level alignment links from source characters to target characters, in addition to  translated target language sentences.
%
Our scripts derive word alignments from the character alignments returned by the Bing Translator API.

\subsection{Russian-English Post-Editing Interface}

@@

\subsection{Spanish-English Post-Editing Interface}

Participants post-edited one text using the interface where alignment links were shown and the other text using the interface where alignment links were omitted. 
%
Participants post-edited the two texts in one session lasting less than one hour. 
%
Post-editors 7 and 9 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
%
Post-editors 8 and 10 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.

@@

Participants performed the test individually in an office setting and were instructed to minimally post-edit. 
%
Specifically, participants were asked to disregard issues of style and to focus on 
%
a) how well the translation conveyed the meaning of the source text, and 
%
b) the grammatical correctness of the translated segments. 
%
Participants sat in front of a computer that displayed the source texts divided up into segments (see Figure \ref{fig:screenshot_true} \vpageref[above]{fig:screenshot_true}). % (see \citet{2014_WMT_Schwartz_etal}).
%
Directly below each source text segment, its machine translation was displayed.
%
Below that was an active response area, where participants were asked to carry out the post-editing.

During initial data collection (the Russian-English condition), the only data collected was the final post-edited output and the overall time taken per text.
%
Subsequently, we enhanced the post-editing software with additional logging functionality, enabling the software to record key-logging and mouse-logging data.
%
For the subsequent Spanish-English condition, this enhanced software was utilized; for this condition millisecond-precision keyboard-event and mouse-event logs were recorded in addition to collecting final post-edited output and overall time taken per text.

We believe that scientific inquiry is at its strongest when experiments can be easily replicated, and when the raw and processed data from such experiments can be directly verified by reviewers, readers, and other experimenters.
%
In that spirit, all data and code produced or used in this work are provided in the attached dataset and software supplements.
%
This includes all logs, along with raw machine translation output, alignment data, post-edited output, adequacy judgements, post-editing software, and supplementary scripts.

### 2015-02-27 paper/paper_results.tex
More work

@@

An experienced English-Russian translator and grader rated all post-edited segments as well as the MT segments.%
%
\footnote{We include these adequacy judgements, along with the other data and code produced or used in this work, in the attached dataset and software supplements.}
%in both human-readable tabular form and machine-readable CSV form in the attached dataset supplement.}
%
The rater was presented with blocks of 10 lines arranged in a vertical list:
%
the first line was a source segment, 
%
the second was its reference translation, and 
%
below these were eight translations for the segment 
%
(the MT, one monolingual post-edited translation from \citet{2014_WMT_Schwartz_etal}, and six bilingual post-edited translations) 
%
listed in random order. 
%
The rater was asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines}) ranging from 2 (translation makes no sense) to 12 (translation is superior to the reference translation).

\todo[inline]{Add Spanish paragraph here}

@@

\todo[inline]{Add Spanish paragraph here}

@@

In addition to rating each post-edited translation, our bilingual human judge rated the adequacy of the unedited MT segments.
%
We thereby obtained direct human judgements of MT quality.%
%
\footnote{Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.}
%
We partition the data according to the MT quality as measured by our human judge in terms of adequacy.
%
For each partition, we then calculate the mean adequacy score of post-edited segments, once for the case where post-editors were presented with alignment data, and once for the case where alignments were not presented.
%
In addition, we perform the same average calculation for the monolingual post-edited segments of Docs A and B from \citet{2014_WMT_Schwartz_etal}.
%
The results are shown in Figure \Vref{fig:mean_adequacy_score}.

>>>>

\subsection{Rating Adequacy of Russian-English}

An experienced English-Russian translator and grader rated all post-edited segments as well as the MT segments.%
%in both human-readable tabular form and machine-readable CSV form in the attached dataset supplement.}
%
The rater was presented with blocks of 10 lines arranged in a vertical list:
%
the first line was a source segment, 
%
the second was its reference translation, and 
%
below these were eight translations for the segment 
%
(the MT, one monolingual post-edited translation from \citet{2014_WMT_Schwartz_etal}, and six bilingual post-edited translations) 
%
listed in random order. 
%
The rater was asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines_russian}) ranging from 2 (translation makes no sense) to 12 (translation is superior to the reference translation).

\subsection{Rating Adequacy of Russian-English}

One experienced Spanish-English translator and grader and one Spanish-English bilingual rated all post-edited segments as well as the MT segments.
%
They did this in cooperation.
%
The raters were presented with blocks of six lines arranged in a vertical list: the first line was a source segment, the second was its machine translation, and below these were four translations for the segment listed in random order.
%
The raters were asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines_spanish}) ranging from 2 (translation makes no sense) to 10 (the meaning of the Spanish sentence is fully conveyed in the English translation). 
% 
For the rating of the segments in this experiment the top category used for the evaluation of the Russian segments was removed because in the Spanish experiment we did not use a reference translation.

@@

\subsection{Russian-English Adequacy}

@@

\subsection{Spanish-English Adequacy}

The mean adequacy score when Spanish bilingual participants were presented with alignments was 8.65. When alignments were omitted from the post-editing tool, the mean adequacy score was 8.57. These means were not significantly different.

\subsection{Analysis}

@@

In addition to rating each post-edited translation, our bilingual human judge rated the adequacy of the unedited MT segments.
%
We thereby obtained direct human judgements of MT quality.%
%
Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.

We partition the data according to the MT quality as measured by our human judge in terms of adequacy.
%
For each partition, we then calculate the mean adequacy score of post-edited segments, once for the case where post-editors were presented with alignment data, and once for the case where alignments were not presented.
%
In addition, we perform the same average calculation for the monolingual post-edited segments of Docs A and B from \citet{2014_WMT_Schwartz_etal}.
%
The results are shown in Figure \ref{fig:mean_adequacy_score}.
